HTW Full w/Code

### 2024-05-20 Manuscript/manuscript.qmd
update htw_full to match dissertation version

---
title: "HTW"
short-title: "Variability and Extrapolation"
date: 04-02-2024
author:
- name: Thomas Gorman
  affiliation: Indiana University
  url: www.tegorman13.github.io
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Rob Goldstone
  affiliation: Indiana University
  url: www.pc.cogs.indiana.edu 
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
abstract: |
  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations. 
keywords:
  - Learning Generalization
  - Function Learning
  - Visuomotor learning
  - Training Variability
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/htw>"
bibliography: ../Assets/Bib/Dissertation.bib
link-citations: true
---

>>>>

---
title: "HTW"
short-title: "Variability and Extrapolation"
date: 04-02-2024
author:
- name: Thomas E. Gorman
  affiliation: Indiana University
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: 0000-0001-5366-5442
- name: Robert L. Goldstone
  affiliation: Indiana University
  url: https://pc.cogs.indiana.edu/
  email: rgoldsto@indiana.edu
  orcid: 0000-0001-8357-8358
abstract: |
  In project 1, we applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. Project 2 also places a greater emphasis on extrapolation performance following training - as varied training has often been purported to be particularly beneficial in such situations. 
keywords:
  - Learning Generalization
  - Function Learning
  - Visuomotor learning
  - Training Variability
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/htw>"
bibliography: ../Assets/Bib/Dissertation.bib
link-citations: true
---

### 2024-05-20 Model/htw_model.qmd
tweaks
update htw_full to match dissertation version

```{r}
#| label: fig-ee-e1
#| fig-caption: conditional and marginal effects
#| fig-height: 8
#| fig-width: 10

@@

p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")

@@

p_ce_1 / p_em_1
```

@@

p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
                         effects = "Model:condit", 
                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
     points=FALSE,plot=FALSE)$`Model:condit` + 
     labs(x="Model",y="Model Error", title="E3. Model Error") + 
     theme(legend.position="right") + 
     scale_color_manual(values=wes_palette("Darjeeling1"))

>>>>

```{r}
#| label: fig-ee-e1
#| fig-cap: A-C) Conditional effects of Model (ALM vs EXAM) and Condition (Constant vs. Varied). Lower values on the y axis indicate better model fit. D) Specific contrasts of model performance comparing 1) EXAM fits between constant and varied training; 2) ALM vs. EXAM for the varied group; 3) ALM fits between constant and varied. Negative error differences indicate that the term on the left side (e.g. EXAM Constant) tended to have smaller model residuals. 
#| fig-height: 8
#| fig-width: 10

@@

#p_ce_1 <- (p1 + p2+ p3) + plot_annotation(tag_levels = c('A'), tag_suffix=".")

@@

#p_ce_1 / p_em_1

(p1 + p2+ p3) /p_em_1 + plot_annotation(tag_levels = c('A'), tag_suffix=".")
```

@@

p_e3 <- plot(conditional_effects(e3_ee_brm_ae, 
                         effects = "Model:condit", 
                         conditions=make_conditions(e3_ee_brm_ae,vars=c("bandOrder"))),
     points=FALSE,plot=FALSE)$`Model:condit` + 
     labs(x="Model",y="Model Error", title="E3. Model Error", fill=NULL, col=NULL) + 
     theme(legend.position="right") + 
     scale_color_manual(values=wes_palette("Darjeeling1"))

### 2024-05-20 Sections/Intro.qmd
update htw_full to match dissertation version

The study of human function learning investigates how people learn relationships between continuous input and output values.  Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with a an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].

@@

To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM). Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the the ability of these influential models of function learning to account for both the group level and individual level data.

>>>>

The study of human function learning investigates how people learn relationships between continuous input and output values.  Function learning is studied both in tasks where individuals are exposed to a sequence of input/output pairs [@deloshExtrapolationSineQua1997; @mcdanielEffectsSpacedMassed2013], or situations where observers are presented with an incomplete scatterplot or line graph and make predictions about regions of the plot that don't contain data [@ciccioneCanHumansPerform2021; @courrieuQuickApproximationBivariate2012; @saidExtrapolationAccuracyUnderestimates2021;@schulzCommunicatingCompositionalPatterns2020].

@@

To account for the empirical results, we will apply a series of computational models, including the Associative Learning Model (ALM) and the Extrapolation-Association Model (EXAM). Notably, this study is the first to employ approximate Bayesian computation (ABC) to fit these models to individual subject data, enabling us to thoroughly investigate the full range of posterior predictions of each model, and to  examine the ability of these influential models of function learning to account for both the group level and individual level data.
